Measuring Directionality in Double Beta Decay and Neutrino Interactions with Kiloton-Scale Scintillation Detectors

### 2013-07-19 Direction.tex
Changed DC QE sentence. --Christoph

The sphere surface is used as the photodetector. It is treated as fully absorbing (no reflections) with a coverage of 100~\%. Two important photodetector properties have also been varied: Transit time spread (TTS, default $\sigma$ = 0.1~ns) and wavelength-dependent quantum efficiency (QE) for photoelectron production. The default is the bialkali photocathode of the Double Chooz photomultiplier tubes (PMTs) \cite{tbd}. It has been verified to be the same type as the KamLAND photocathode. We used the Double Chooz QE because the data was available with finer spacing in wavelength.

>>>>

The sphere surface is used as the photodetector. It is treated as fully absorbing (no reflections) with a coverage of 100~\%. Two important photodetector properties have also been varied: Transit time spread (TTS, default $\sigma$ = 0.1~ns) and wavelength-dependent quantum efficiency (QE) for photoelectron production. Default is the QE of a bialkali photocathode (Hamamatsu R7081 PMT), digitized values come from the Double Chooz \cite{dctwo} Monte Carlo simulation. The KamLAND 17 inch PMTs use the same photocathode type (bialkali) with similar quantum efficiency.
